### 2020-03-07 draft_ABP.tex
merge from overleaf

($A_n$ (sting integral?), $B_n$ (Shi arrangement?), or both from $F$-polynomial)

For example, $A_n$ type cluster configuration spaces come from original string 
amplitudes
\[
	\int_{z_1<z_2<\cdots <z_n}
	\frac{\mathrm dz_2\cdots \mathrm dz_{n-2}}{(z_1-z_2)\cdots (z_{n-2}-z_{n-1})}
	\prod_{i<j} (z_i-z_j)^{\alpha' s_{ij}},
\]
where we fix the gauge by setting $z_1=0$, $z_{n-1}=1$ and $z_n=\infty$.
The $u$-variables of this configuration space are
\[
	u_{ij}=\frac{(z_{i-1}-z_j)(z_i-z_{j-1})}{(z_i-z_j)(z_{i-1}-z_{j-1})},
\]
and they satisfy the $u$-equations
\[
	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
\]
where $(i,j)\not\sim (k,l)$ means that diagonals $(i,j)$ and $(k,l)$ of
$(n+3)$-gon are crossed.

(Zhenjie: we should use another parametrization of $A_n$) 
(mention hyperplane arrangement)

$B_n$: Shi arrangement

The Shi arrangement of $B_n$ contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
on the real line with the freedom corresponding to the global transformation 
$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
given by the following hyperplains
\[
    z_i-z_j=0\quad \text{and}\quad z_i-z_j=1,
\]
for $1\leq i<j\leq n+1$.

The the $u$ variables of $B_n$ can be solved by these $z_i$ by 
\[
    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
\]
and 
\[
\begin{aligned}
    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
\end{aligned}
\]
where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.

>>>>

For example, $A_n$ type cluster configuration spaces come from original string 
amplitudes
\[
	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n}
	\frac{\mathrm dz_2\cdots \mathrm dz_{n-2}}{(z_1-z_2)\cdots (z_{n-2}-z_{n-1})}
	\prod_{i<j} (z_j-z_i)^{\alpha' s_{ij}},
\]
where we fix the gauge by setting $z_1=0$, $z_{n-1}=1$ and $z_n=\infty$.
It's not in the form of stringy integrals, but we can use a positive
parametrization 
\[
z_3=1+x_2,\quad z_4=1+x_2+x_3,\quad \dots, \quad 
z_{n-1}=1+x_2+\cdots+x_{n-2}
\]
to rewrite the integral $\mathcal I_n$, then
\[
    \mathcal I_n=\int_{\mathbb R_+^{n-3}}
	\frac{\mathrm dx_2\cdots \mathrm dx_{n-2}}{x_2\cdots x_{n-2}}
	\prod_{i<j} p_{ij}^{\alpha' s_{ij}},
\]
where $p_{ij}=x_i+\cdots+x_{j-1}$. The $u$-variables of this configuration space are
\[
	u_{ij}=\frac{p_{i-1,j}p_{i,j-1}}{p_{ij}p_{i-1,j-1}},
\]
and they satisfy the $u$-equations
\[
	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
\]
where $(i,j)\not\sim (k,l)$ means that diagonals $(i,j)$ and $(k,l)$ of
$(n+3)$-gon are crossed.

Another example still comes from a hyperplane arrangement, the Shi arrangement,
which is also $B_n$ type cluster stringy integral.
The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
on the real line with the freedom of global transformation 
$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
given by the following hyperplains
\[
    z_i-z_j=0\quad \text{and}\quad z_i-z_j=1,
\]
for $1\leq i<j\leq n+1$. Its stringy integral is
\[
	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n<0}
	\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(z_1-z_2)\cdots (z_{n}-z_{n+1})}
    \prod_{1\leq i<j \leq n}(z_j-z_i)^{s_{ij}}|z_i-z_j-1|^{t_{ij}}
\]
(Zhenjie: Carefully check the notation!)
The $u$-variables of this configuration space are
\[
    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
\]
and 
\[
\begin{aligned}
    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
\end{aligned}
\]
where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.
